%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{ROHIT}{UPADHYA}{
\href{mailto:rohitupadhya18@gmail.com}{\Letter\ rohitupadhya18@gmail.com}\ \ \
\href{}{\faMobile\ +91-8134082213/+91-9615422513} \ \ \
\href{https://github.com/nocturnalnocturnal}{\faGithub\ nocturnalnocturnal}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 




\subsection{National Institute of \\Technology, Silchar} 
\descript{B.Tech. in Computer Science and Engineering}
\location{Expected May 2019}

\location{CGPA : 8.23 / 10 \\
(as of 5$^{th}$ Semester.)}
\sectionsep

\subsection{South Point School, \\Guwahati}
\location{AISSCE 2014, CBSE | Guwahati, India. \\Percentage : 92.2
}
\sectionsep


\subsection{St.Edmund's School, \\Shillong.}
\location{ICSE 2012, CISCE | Shillong, India. \\ Percentage : 91.6
}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}


\subsection{Undergraduate}

Data Structures \\
Object Oriented Design \\
Discrete Structures \\
Signals \& Data Communication \\
Computer Graphics \\
Formal Languages and Automata Theory\\
Stochastic Processes\\
Microprocessors \& System Programming\\
Computer Networks\\
Computer Architecture and Organization

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\location{Proficient}
Java \textbullet{}   C \textbullet{} \LaTeX{}   \\ 
\location{Intermediate}
Android \textbullet{} CSS \textbullet{}HADOOP \textbullet{}JavaScript \textbullet{}Nodejs \textbullet{} SageMath\\
\location{Familiar:}
MATLAB 

\section{Areas of Interest}
 Big Data, Cyber Security, Android App Development, Core Java, Algorithms

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS}



\runsubsection{Big data processing using Hadoop MultiClusters}

\descript{NIT Silchar}
\location{Guide: Mr. Ripon Patgiri, NIT Silchar.}
\location{December 2016 – February 2017}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
    \item Performed a detailed analysis of the HADOOP framework.
    \item Successfully connected 37 computers using the HADOOP Framework.
    \item Was successful in writing and executing various programs in the multi-cluster.
    \item Delivered a brief lecture on Big Data and HADOOP.
\end{tightemize}
\sectionsep

\runsubsection{TEDx NIT Silchar Website | \href{https://github.com/nocturnalnocturnal/TEDx-Website}{\faGithub} }

\descript{NIT Silchar}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
    \item Developed an interactive website for TEDx NIT Silchar, 2016.
    \item Technologies Used : 
    \vspace{\topsep}
        \begin{tightemize}
            HTML \textbullet{}JavaScript \textbullet{}CSS \textbullet{} Bootstrap Framework
        \end{tightemize}
\end{tightemize}
\sectionsep



\section{Research Work}

\runsubsection{Study and Analysis of Lightweight Stream Ciphers | \href{https://github.com/nocturnalnocturnal/Some-standard-Stream-Ciphers-and-Study-and-Analysis-of-these-Stream-Ciphers}{\faGithub}}
\descript{NEHU, Shillong}
\location{16$^{th}$May 2017 - 29$^{th}$ June 2017}
\location{Guide : Dr.B.Bhuyan, NEHU Shillong.}
\vspace{\topsep}
\begin{tightemize}
    \item Objective :Detailed analysis and implementation of Feedback Shift Registers, Stream Ciphers and Attacks on them.
    \item Analysis will help in making a better Cipher.
    \item Performed an attack on one of the ciphers.
    \item Studied various papers related to different Ciphers and also the Mathematics involved.
    \item Wrote a detailed report in \LaTeX{} on various LFSRs, Ciphers and Attacks performed of Ciphers during the internship period.
\end{tightemize}
\sectionsep

\runsubsection{Book Chapter}\\
\descript{Chapter Name\ : \ Applicability of Lightweight Stream Cipher in Crowd Computing: A detailed Survey and Analysis}
\location{Co-authors : Dr.B.Bhuyan, NEHU Shillong, Mr.Subhrajyoti Deb, NEHU Shillong.}
\vspace{\topsep}
\begin{tightemize}
    \item Accepted in the book \emph{Crowd Assisted Networking and Computing}  to be published by by \emph{CRC Press, Taylor \& Francis, USA}.
    \item Book edited by Al-Sakib Khan Pathan, Associate Professor, Department of Computer Science and Engineering, Southeast University, Dhaka, Bangladesh.
    \item Online version will be out soon.
\end{tightemize}
\sectionsep


\end{minipage}
\newpage
\begin{minipage}[t]{0.33\textwidth}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\section{ACHIEVEMENTS} 
    \item Stood 8$^{th}$ in ICSE(10$^{th}$ Board), 2012 \\in the State of Meghalaya, India.
    \item Accredited with A+ in Core Java by \\HPES held in NIT Silchar(January 2016).
    \item Accredited with A in Android App \\Development by HPES(May-June 2016).
\sectionsep






\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.60\textwidth}

\section{EXPERIENCE}
\runsubsection{Executive Member}
\descript{| Computer Science Society, NIT Silchar.}
\location{2017-2018}
\sectionsep

\runsubsection{Research Intern}
\descript{| NEHU, Shillong.}

\location{May 2017 - June 2017}
\sectionsep

\runsubsection{Core Team Member \& Website Developer}\\
\descript{ TEDx NIT Silchar}
\location{November, 2016}
\sectionsep

\runsubsection{Instructor of C classes of Freshmen in NIT Silchar}
\descript{}

\location{2016-2017}
\sectionsep

\runsubsection{Core Java Trainee}
\descript{| HP Education Service}
\location{January ,2016}
\sectionsep

\runsubsection{Android App Development Trainee}
\descript{| HP Education Service}
\location{Kolkata Batch of Summer 2016}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\end{minipage}
\end{document}